Assessing variations in the chemistry of fossil- and modern-*Pinus* pollen

### 2021-06-25 manuscript.Rmd
excluding docx from tracking, changed a sentence in FPA section

---
title: 'Assessing variations in the chemistry of fossil- and modern-*Pinus* pollen'
date: '2020/02/04'
output:
  bookdown::pdf_document2:
    toc: false
    extra_dependencies: ["flafter"]
bibliography: references.bib
csl: biology-letters.csl
---

@@

One of key challenges faced by chemical palynologists using micro-FTIR and other approaches is the time taken to extract and analyse fossil-pollen samples.
Some microscopes are equipped with automated stages, where multiple point locations on the slide can be targeted manually to record spectra automatically.
However, recent developments in technologies related to FTIR may allow for easier and faster capture of spectra of pollen grains.
A focal plane array detector (FPA) allows capture of an image and matrix of spectra over the same sample area instead of a single spectra at a specific point/area [@zimmermannAnalysisAllergenicPollen2016;@zimmermannChemicalCharacterizationIdentification2018; @zimmermannVibrationalMicrospectroscopyEnables2015].
This enables the extraction of spectra from several single grains from the same area on the sample without the need to relocate the detector of the microscope or move the slide, and is therefore of potentially high relevance for palaeoecological research.
When combined with imaging processing technology, it may allow for more rapid identification and generation of FTIR spectra of pollen grains from sediment samples, but whilst FTIR spectroscopy using FPA detectors have been widely applied with microplastics [@loderEnzymaticPurificationMicroplastics2017; @machadoMicroplasticsEmergingThreat2018; @primpkeAutomatedApproachMicroplastics2017] and some studies on pollen [@chiappePollenGrainsFunctionalized2017], there has been limited investigation into their application on fossil-pollen residues taken from sediment cores.

>>>>

---
title: 'Assessing variations in the chemistry of fossil- and modern-*Pinus* pollen'
date: '2020/02/04'
output:
  bookdown::word_document2:
  bookdown::pdf_document2:
    toc: false
    extra_dependencies: ["flafter"]
bibliography: references.bib
csl: biology-letters.csl
---

@@

One of key challenges faced by chemical palynologists using micro-FTIR and other approaches is the time taken to extract and analyse fossil-pollen samples.
Some microscopes are equipped with automated stages, where multiple point locations on the slide can be targeted manually to record spectra automatically.
However, recent developments in technologies related to FTIR may allow for easier and faster capture of spectra of pollen grains.
A focal plane array detector (FPA) allows capture of an image and matrix of spectra over the same sample area instead of a single spectra at a specific point/area [@zimmermannAnalysisAllergenicPollen2016;@zimmermannChemicalCharacterizationIdentification2018; @zimmermannVibrationalMicrospectroscopyEnables2015].
This enables the extraction of spectra from several single grains from the same area on the sample without the need to relocate the detector of the microscope or move the slide, and is therefore of potentially high relevance for palaeoecological research.
When combined with imaging processing technology, it may allow for more rapid identification and extraction of FTIR spectra of pollen grains from sediment samples.
Whilst FTIR spectroscopy using FPA detectors have been widely applied with microplastics [@loderEnzymaticPurificationMicroplastics2017; @machadoMicroplasticsEmergingThreat2018; @primpkeAutomatedApproachMicroplastics2017] and some studies on pollen [@chiappePollenGrainsFunctionalized2017], there has been no investigation into application of FPA detectors on fossil-pollen residues taken from sediment cores.
